Recent demography drives changes in linked selection across the maize genome

### 2015-11-13 manuscript.tex
FINAL FINAL FINAL

\significancetext{
Both selection and demographic change play important roles in
shaping diversity across the genome, but there are few clear empirical examples of the interplay of these two forces. Here we document the combined effects of demography and linked selection on genome-wide diversity in domesticated maize and its wild ancestor teosinte. We estimate that although maize underwent a bottleneck to ≈ 5\% of the size of the ancestral teosinte population, recent expansion has resulted in a maize population much larger than teosinte. Positive selection on new genic mutations has had relatively little effect on genetic diversity, but selection against deleterious mutations has dramatically reduced diversity in and immediately around genes in both taxa. The relative impact of selection depends on the age of the polymorphisms evaluated, revealing that a complete understanding of genome-wide patterns of diversity requires careful assessment of both demographic history and the effects of linked selection.
} %JRI

>>>>

\significancetext{
Both selection and demographic change play important roles in shaping genetic diversity, but there are few empirical examples of the interplay between these forces. We document the combined effects of demography and linked selection on maize genome-wide diversity. After going through a bottleneck ≈5\% of the size of the ancestral teosinte population, recent expansion resulted in a maize population much larger than teosinte. Positive selection on new genic mutations has affected genetic diversity little, but selection against deleterious mutations dramatically reduced diversity within and surrounding genes. The impact of selection depends on the age of the polymorphisms evaluated, revealing that a complete understanding of genome-wide diversity requires careful assessment of demographic history and the effects of linked selection.
} %JRI
